\documentclass{onkursen-resume}

\pagestyle{fancy}
\lhead{onkursen@gmail.com\\ \noindent (918) 407$-$2319}
\rhead{onkursen.com\\ \noindent github.com/onkursen}
\chead{{\bf \Huge Onkur Sen}}
\lfoot{}
\cfoot{}
\rfoot{}

%\usepackage[default,osfigures,scale=0.95]{opensans} %% Alternatively
%%% use the option 'defaultsans' instead of 'default' to replace the
%%% sans serif font only.
%\usepackage[T1]{fontenc}


\begin{document}

\begin{multicols}{2}

\section*{Education}

\noindent {\bf \large Stanford University}\\
September 2014 | June 2016 (expected)\\
M.S. Computer Science\\
Depth 1: Artificial Intelligence (AI)\\
Depth 2: Human-Computer Interaction (HCI)\\

\vspace{6mm}

\noindent {\bf \large Rice University}\\
August 2010 | May 2013\\
B.S. Physics\\
B.A. Mathematics\\
Minor: Computational and Applied Mathematics

\end{multicols}

\vspace{-2mm}

\hr

\section*{Software Engineering Experience}

\affiliation{Accompany}{Software Engineer Intern}{Ruby/Rails, C++, SQL}{June 2015 | September 2015}
\begin{itemize*}
\item Built an end-to-end pipeline from scratch for automatically crawling, extracting, vetting, and ranking news feeds
\item Implemented algorithm to cluster news articles based on similarity and relevance in article titles and contents
%\item Implementing algorithm that clusters news articles on similar titles to improve relevance
\end{itemize*}
\vspace{-1mm}

\affiliation{Palantir}{Forward Deployed Engineer (Philanthropy Team)}{Java, Groovy, SQL, Python}{May 2013 | September 2014} 
\begin{itemize*}
\item Developed custom dashboard visualizations of commitments by the Clinton Global Initiative (CGI) over the past ten years
\item Maintained and upgraded infrastructure for the National Center for Missing and Exploited Children (NCMEC)
\end{itemize*}
\vspace{-1mm}

\affiliation{Plum District}{KPCB Engineering Fellow}{Ruby/Rails}{May 2012 | August 2012}
\begin{itemize*}
%\item Implemented tracking mechanism for Remarketing, Omniture, and Google Analytics
\item Corrected redemption of vouchers and allowed view of past offers in business center
\end{itemize*}
\vspace{-1mm}

\affiliation{TripAdvisor}{Software Engineer Intern}{Java/Velocity}{December 2011 | January 2012}
\begin{itemize*}
\item Removed cross-site scripting (XSS) vulnerabilities and improved display of Facebook likes, ratings, and recommendations
\end{itemize*}
\vspace{-1mm}

\hr

\section*{Research}

\affiliation{Carta}{Advisors: Dr. Michael Bernstein and Dr. Ramesh Johari, Stanford University}{Python, Ruby/Rails, SQL}{Fall 2014 | Present}
\begin{itemize*}
\item Implementing web app that uses machine learning algorithm to provide course recommendations for students
\end{itemize*}
\vspace{-1mm}

\affiliation{Apparition: Crowdsourced User Interfaces That Come To Life As You Sketch Them}{Advisor: Dr. Michael Bernstein, Stanford University}{JavaScript (Meteor)}{Winter 2014 | Fall 2014}
\begin{itemize*}
\item Developed web application that utilizes crowdsourcing around a Method Draw canvas to quickly prototype interfaces
\end{itemize*}
\vspace{-1mm}

\affiliation{Searching for Supersymmetric Top Quarks at the Large Hadron Collider (LHC)}{Advisor: Dr. Paul Padley, Rice University}{Python}{Fall 2012 | Spring 2013}
\begin{itemize*}
\item Used boosted decision trees to isolate decay of stop quarks from background top-top interactions
%\item Extended on phenomenological data and theory from Bhaskar Dutta et al. (Texas A\&M)
\item {\bf Publication:} Sen, O. and Padley, B.P. Searching for Supersymmetric Top Quarks at the LHC [Thesis]. April 22, 2013.
\end{itemize*}
\vspace{-1mm}

\affiliation{Melody Analysis and Harmony Generation}{Advisor: Dr. Kurt Stallmann, Rice University}{Python}{Fall 2011 | Fall 2012}

\begin{itemize*}
\item Determined key of input score given only melodic line and generated complementary harmonic progression
\item {\bf Publication:} Sen, O. and Stallmann, K. Analysis of Melody Through Key Definition and Generation of Complementary Harmonies. Rice Undergraduate Research Symposium. Houston, TX, April 13, 2012.
\end{itemize*}
\vspace{-1mm}

\affiliation{Computationally Generating Musical Variations}{Advisor: Dr. Sandip Sen, University of Tulsa}{Java}{Fall 2009 | Fall 2011}

\begin{itemize*}
\item Created systematic framework for representing musical scores and used genetic algorithms to create variations on themes
\item {\bf Publication:} Sen, O. Creating Musical Variations Using Genetic Algorithms. {\em American Junior Academy of Sciences} 2011.
\end{itemize*}
\vspace{-1mm}

\affiliation{Social Networks and Norm Emergence}{Advisor: Dr. Sandip Sen, University of Tulsa}{Java}{Fall 2008 | Summer 2009}

\begin{itemize*}
\item Analyzed comparative speed of emergence of a norm in social networks with different topologies and behavioral patterns
\item {\bf Publication:} Sen, O. and Sen, S. Effects of Social Network Topology and Options on Norm Emergence. {\em Lecture Notes in Artificial Intelligence} Vol. 6069, p. 211$-$222, Springer-Verlag, 2010.
\end{itemize*}
 
%\affiliation{Social Dilemmas and Aspiration Levels}{Advisor: Dr. Sandip Sen, University of Tulsa}{Java}{Fall 2007 | Summer 2009}
%
%\begin{itemize*}
%\item Developed algorithmic approach to solve the Tragedy of the Commons in a multi-agent system using aspiration levels
%\item {\bf Publication:} Sen, O. and Sen, S. Solving the Tragedy of the Commons by Adapting Aspiration Levels. {\em Proceedings of COIN@IJCAI09} 2009.
%\end{itemize*}

\hr

\section*{Projects}

\noindent
\begin{tabularx}{\textwidth}{Xlrr}
\project{onkursen.com}{Personal website}{Jekyll}{2012 | Present}
\project{Road Trip Recommendations}{Using regressions for Yelp restaurant recommendations}{Python}{Fall 2014}
\project{Contagion}{Modeling disease spread across social networks (Palantir Hack Week)}{Python, D3}{Summer 2013}
\project{Predicting Terrorist Attacks}{Comparing models on the Global Terrorism Database}{Python}{Spring 2013}
\project{All About Inverses}{A talk that gives a concise primer on linear algebra}{reveal.js}{Summer 2012}
\project{Sangleet}{wrote/choreographed/directed a 15-minute musical}{SoundCloud}{Spring 2011}
\end{tabularx}

%\project{Rice University Catalyst}{website}{catalyst.rice.edu}{HTML/CSS}{2011|2013}
%\project{Rice University South Asian Society}{website}{sas.rice.edu}{HTML/CSS}{2011|2013}

\end{document}